Simulation studies

### 2020-06-18 manuscript/manuscript/simulation_study_results.Rmd
add figures

#### Recall curves 
__Nudging dataset__
```{r}
include_graphics("../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf")
```
<embed src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf" width="50%" style="display: block; margin: auto;" type="application/pdf" />

<img src="../../results/one_seed/plots/nudging/inclusion_all_nudging.pdf"
     style="float: left; margin-right: 10px;" />
__PTSD dataset__

>>>>

#### Recall curves 
__Nudging dataset__

__PTSD dataset__
